R, Python, and Ruby clients for GBIF species occurrence data

### 2020-02-25 use-cases/city-diversity.Rmd
attempt wicket fix
install stuff
tweaks to use cases

```{r include=FALSE}
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  fig.width = 8,
  fig.height = 6,
  cache.path = "cache/"
)
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  fig.width = 8,
  fig.height = 6,
  cache.path = "cache/"
)
```

### 2020-02-25 use-cases/oak-occurrences.Rmd
install rnaturalearth
install stuff
tweaks to use cases

```{r include=FALSE}
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  cache.path = "cache/"
)
```

This example comes from [Antonio J. Perez-Luque](https://twitter.com/ajpelu) who [shared his plot on Twitter][tweet]. Antonio compared the occurrences of Valley Oak (_Quercus lobata_) from [GBIF][gbif] to the distribution of the same species from the [Atlas of US Trees][atlas].

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  cache.path = "cache/"
)
```

This example is inspired by a tweet from [Antonio J. Perez-Luque](https://twitter.com/ajpelu) who [shared his plot on Twitter][tweet]. Antonio compared the occurrences of Valley Oak (_Quercus lobata_) from [GBIF][gbif] to the distribution of the same species from the [Atlas of US Trees][atlas].

The data in question from the example above is no longer available, so below
we use a different species.
